Mixture-of-tastes Models for Representing Users with Diverse Interests

### 2018-01-20 paper/paper.tex
Add Wang and Cho (2017) citation.

\citet{athiwaratkun2017multimodal} extend this idea by representing words a mixtures of Gaussians. This allows them to capture polysemy by modelling each word with several distinct, small-variance Gaussian distributions (rather than artificially inflating the variance of a single distribution). This allows much clearer separation of distinct meanings. This work is closest to the approach presented here.

@@

>>>>

\citet{athiwaratkun2017multimodal} extend this idea by representing words a mixtures of Gaussians. This allows them to capture polysemy by modelling each word with several distinct, small-variance Gaussian distributions (rather than artificially inflating the variance of a single distribution). This allows much clearer separation of distinct meanings.

@@

The approach closest to the one presented here, but focusing solely on the sequence-based setting, is presented in \citet{wang2017attention}, and was published contemporaneously with the writing of this paper. The authors use pre-trained and fixed item embeddings, recurrent neural networks with attention to model user sequences, and either feedforward or recurrent decoders to generate taste mixture components. They find that both attention and recurrent decoders improve the recommendation results. We suggest that the two papers should be seen are mutually reinforcing and complementary, and suggest that a combination of both approaches (recurrent decoders and end-to-end embedding training) would be beneficial.
